---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# foofactors

<!-- badges: start -->
<!-- badges: end -->

This package is made as final project for Spatial data with R.
It has function "storetrack3" which creates object of a class "mytrack" and is
used to store name, timestamps, CRS and coordinates of a track.
In addition to this, object of a class "myclass" have print, plot and summary
methods and one additional method for calculating distance of the track called
"distance2".

## Installation

You can install this package with:

``` r
install.packages("foofactors")
```

## Example

This example shows how to create object of a type "mytrack". We have coordinates
of two cities, Madrid and Kyiv:

```{r example1}
library(foofactors)
test_object <- storetracks3("Madrid-Kyiv", c("2009-12-25 18:39:21 CST",
                                              "2009-12-25 18:39:31 CST"),
                              4326,
                              data.frame(lon=c(-3.761989,30.415929),lat=c(40.415190,50.470800))
  )
```

In the above example, 4326 is code for WGS84 Geoid. Another code can be used as well. We can calculate distance with or without using S2. To use S2 we type:
```{r example2}
distance2(test_object,TRUE)
```

Or for distance without S2 we type:
```{r example3}
distance2(test_object,FALSE)
```

Package also uses few of the methods generate from existing generic functions,
for example plot, print and summary.

### "print" method prints information about what is stored in the object's slots
```{r example4}
print(test_object)
```

### "summary" method will summarize how many points we have stored in our object
```{r example5}
summary(test_object)
```

### "plot" method plots line graph, with the line connecting subsequent points.
```{r example6}
plot(test_object)
```
