---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# foofactors

<!-- badges: start -->
<!-- badges: end -->

This package is made as final project for Spatial data with R. Package is focused
on two classes: 

* **mytrack** object which will hold some metadata for a line as well as coordinates of points of
a line
* **multitracks** object which is intended to be a container for multiple objects of a class
**mytrack**

**mytrack** has the following methods included:

* *print* which prints metadata and coordinates of points
* *summary* gives count of points in line
* *plot* plots line
* *distance* calculates distance of the line either on flat surface(S2 is FALSE) or
on a sphere(S2 is TRUE)

**multitracks** has the following methods included:

* *print* will print names of all tracks in the container
* *summary* will provide with number of tracks in container, their names, number of points
they have and the distance on S2.
* *addlist* adds new line of class **mytrack** to container of class **multitracks**

### Installation

You can install this package with:

``` r
install.packages("foofactors")
```

### Example for class *mytrack*

This example shows how to create object of a type **mytrack**. We have coordinates
of two cities, Madrid and Kyiv, and use function **storetracks** to create the object:

```{r example1}
library(foofactors)
test_object1 <- storetracks("Madrid-Kyiv", c("2009-12-25 18:39:21 CST",
                                              "2009-12-25 18:39:31 CST"),
                              4326,
                              data.frame(lon=c(-3.761989,30.415929),lat=c(40.415190,50.470800))
  )
```

In the above example, 4326 is code for WGS84 Ellipsoid. Another code can be used as well. We can calculate distance with or without using S2. To use S2 we type:

```{r example2}
distance(test_object1,TRUE)
```

Or for distance without S2 we type:
```{r example3}
distance(test_object1,FALSE)
```

Package also uses few of the methods generate from existing generic functions,
for example plot, print and summary.

**print** method prints information about what is stored in the object's slots
```{r example4}
print(test_object1)
```

**summary** method will summarize how many points we have stored in our object
```{r example5}
summary(test_object1)
```

**plot** method plots line graph, with the line connecting subsequent points.
```{r example6}
plot(test_object1)
```

### Example for class *multitracks*

First we create object of a class **multitracks** and add our first line to it by
using **multitracks** function:
```{r example7}
holder <- multitracks(test_object1)
```

Now we can create second **mytrack** object:
```{r example8}
test_object2 <- storetracks("Moscow-Oslo", c("2009-12-25 19:39:21 CST",
                                              "2009-12-25 20:39:31 CST"),
                              4326,
                              data.frame(lon=c(-3.761989,30.415929),lat=c(40.415190,50.470800))
  )
```

When we want to add a subsequent line to our container, we use method **addlist**, with
first argument being **multitracks** object, and second argument being **mytrack** object:
```{r example9}
addlist(holder,test_object2)
```

As we can see, our container will hold these lines of a **mytrack** class in a **hash**,
type of dictionary structure used in R. Access is made by using key-value system, in this case,
keys would be names of tracks:
```{r example10}
holder$lines
holder$lines$"Moscow-Oslo"
```

Two generic methods used for **multitracks** objects are **print**:
```{r example11}
print(holder)
```

and **summary**:
```{r example12}
summary(holder)
```
